\documentclass[11pt]{article}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

\title{Plant Disease Classification Challenge}
\author{Kaggle Competition}
\date{}

\begin{document}
\maketitle

\section{Overview}

In this competition, participants are tasked with building a machine learning model to classify plant leaf images into one of $K$ disease categories.
Accurate classification is essential for early disease detection and agricultural sustainability.

The dataset consists of labeled RGB images collected under real-world conditions, including variations in lighting, background, and leaf orientation.

\section{Problem Statement}

Given an image $x_i \in \mathbb{R}^{H \times W \times 3}$, predict its corresponding label
\[
y_i \in \{1, 2, \dots, K\}.
\]

Your model should learn a function
\[
f_\theta : \mathbb{R}^{H \times W \times 3} \rightarrow \Delta^{K-1},
\]
where $\Delta^{K-1}$ denotes the $(K-1)$-simplex representing a probability distribution over classes.

\section{Evaluation Metric}

Submissions are evaluated using \textbf{Categorical Cross-Entropy Loss}:

\[
\mathcal{L} = -\frac{1}{N} \sum_{i=1}^{N} \sum_{k=1}^{K}
y_{i,k} \log \hat{p}_{i,k},
\]

where:
\begin{itemize}
    \item $N$ is the number of samples in the validation set,
    \item $y_{i,k}$ is a one-hot encoded ground-truth label,
    \item $\hat{p}_{i,k}$ is the predicted probability for class $k$.
\end{itemize}

Lower scores indicate better performance.

\section{Data Description}

The dataset is split into:
\begin{itemize}
    \item \textbf{Training set}: Labeled images used to train models.
    \item \textbf{Test set}: Unlabeled images used for final evaluation.
\end{itemize}

Each image file name corresponds to a unique identifier used in the submission file.

\section{Submission Format}

Participants must submit a CSV file with the following format:

\[
\texttt{image\_id}, \hat{p}_1, \hat{p}_2, \dots, \hat{p}_K
\]

Each row must satisfy the probability constraint:
\[
\sum_{k=1}^{K} \hat{p}_k = 1.
\]

\section{Baseline Model}

A simple baseline model minimizes empirical risk:

\[
\theta^{*} = \arg\min_{\theta} \;
\mathbb{E}_{(x,y) \sim \mathcal{D}}
\left[ \mathcal{L}(f_\theta(x), y) \right]
+ \lambda \|\theta\|_2^2,
\]

where $\lambda$ is an $L_2$ regularization coefficient.

\section{Rules}

\begin{itemize}
    \item External data is \textbf{not allowed}.
    \item Manual labeling of the test set is prohibited.
    \item Final rankings are determined by performance on the private leaderboard.
\end{itemize}

\section{Getting Started}

Check out the provided starter notebooks for:
\begin{itemize}
    \item Data loading and visualization
    \item Baseline CNN and ViT models
    \item Cross-validation and ensemble techniques
\end{itemize}

Good luck, and happy modeling! 🚀

\end{document}